---
title: "MIS64018-004 Assignment 2 Module4 "
author: "wliu16"
date: "2022-09-22"
output: pdf_document
---

```{r}
#Set working directory, install and load the package lpSolveAPI
setwd("~/Desktop/R/64018/Assignment module 4")
library(lpSolveAPI)
```

Next, we will list the objective function and constraints. 
$$\text{The objective function is to } Max \hspace{.2cm} 
Z = 420(L_1+L_2+L_3)+360(M_1+M_2+M_3)+300(S_1+S_2+S_3)$$
$$\text{which can also be written as }Z = 420 L_1 + 420 L_2 + 420 L_3 + 360 M_1 + 360 M_2 + 360 M_3 + 300 S_1 + 300 S_2 + 300 S_3$$

Subject to the following capacity constraints
$$L_1 + M_1 + S_1 \le 750$$
$$L_2+M_2+S_2 \le 900$$
$$L_3 + M_3 +S_3 \le 450$$
Storage constraints
$$20 L_1 + 15 M_1 + 12 S_1 \le 13000$$
$$20 L_2 + 15 M_2 + 12 S_2 \le 12000$$
$$20 L_3 + 15 M_3 +12 S_3 \le 5000$$
Sale constraints
$$L_1 + L_2 + L_3 \le 900$$
$$M_1 + M_2+ M_3 \le 1200$$
$$S_1 + S_2 + S_3 \le 750$$
Same percentage production among three plants
$$L_1 + M_1 + S_1)/(L_2 + M_2 + S_2)/(L_3+M_3+S_3) = 750:900:450$$
Which can be broken down to
$$(L_1 + M_1 + S_1)/(L_2 + M_2 + S_2) = 750:900$$
$$(L_2 + M_2 + S_2)/(L_3+M_3+S_3) = 900:450$$
Which are equivalent to the following

$$900 L_1+ 900 M_1+ 900 S_1 - 750 L_2- 750 M_2 -750 S_2 = 0$$
$$450 L_2 + 450 M_2 + 450 S_2 - 900 L_3 - 900 M_3 - 900 S_3 = 0$$
Second equation can be further simplified to:
$$L_2 + M_2 + S_2 - 2 L_3 - 2 M_3 - 2 S_3 = 0$$
Non-negativity constraints
$$L_1, L_2, L_3, M_1, M_2,M_3, S_1, S_2, S_3 \ge 0$$
All the 11 constraints as follows:
$$L_1 + 0 L_2 + 0 L_3 +M_1 +0 M_2 +0 M_3 +S_1 + 0 S_2 + 0 S_3 \le 750$$
$$0L_1 + L_2 + 0 L_3 +0 M_1 +M_2 +0 M_3 +0 S_1 + S_2 + 0 S_3\le 900$$
$$0L_1 + 0 L_2 + L_3 +0 M_1 +0 M_2 +M_3 +0 S_1 +0 S_2 +S_3\le 450$$
$$20 L_1 + 0 L_2 +0 L_3 +15 M_1 + 0 M_2 +0 M_3 +12 S_1 +0 S_2 +0 S_3 \le 13000$$
$$0 L_1 + 20 L_2 +0 L_3 +0 M_1 + 15 M_2 +0 M_3 +0 S_1 +12 S_2 +0 S_3  \le 12000$$
$$0 L_1 + 0 L_2 +20 L_3 +0 M_1 + 0 M_2 +15 M_3 +0 S_1 +0 S_2 +12 S_3  \le 5000$$
$$L_1 +  L_2 +  L_3 +0 M_1 +0 M_2 +0 M_3 +0 S_1 + 0 S_2 + 0 S_3 \le 900$$
$$0 L_1 +0  L_2 +0  L_3 + M_1 + M_2 + M_3 +0 S_1 + 0 S_2 + 0 S_3 \le 1200$$
$$0 L_1 +0  L_2 +0  L_3 +0 M_1 +0 M_2 +0 M_3 + S_1 + S_2 + S_3 \le 750$$
$$900 L_1+ 900 M_1+ 900 S_1 - 750 L_2- 750 M_2 -750 S_2 = 0$$
$$ L_2 + M_2 + S_2 - 2 L_3 - 2 M_3 - 2 S_3 = 0$$
Considering the first 9 constraints,
```{r}
library("lpSolve")
f.obj <- c(420,420,420,360,360,360,300,300,300)
f.con <- matrix(c(1,0,0,1,0,0,1,0,0,
                   0,1,0,0,1,0,0,1,0,
                   0,0,1,0,0,1,0,0,1,
                   20,0,0,15,0,0,12,0,0,
                   0,20,0,0,15,0,0,12,0,
                   0,0,20,0,0,15,0,0,12,
                   1,1,1,0,0,0,0,0,0,
                   0,0,0,1,1,1,0,0,0,
                   0,0,0,0,0,0,1,1,1), nrow = 9, byrow = TRUE)
f.dir <- c("<=",
            "<=",
           "<=",
            "<=",
           "<=",
           "<=",
            "<=",
            "<=",
            "<=")
f.rhs <- c(750,
            900,
            450,
            13000,
            12000,
            5000,
            900,
            1200,
            750)

# Final value output
lp("max", f.obj, f.con,f.dir,f.rhs)
 
# Variables final values
lp("max", f.obj, f.con,f.dir,f.rhs)$solution

```

Considering all 11 constraints,
```{r lpcodeœ, results="hide"}
lprec <- make.lp(0,9)  #start with 0 constraint and 9 variables
set.objfn(lprec, c(420, 420, 420, 360, 360, 360, 300, 300, 300))#objective func
lp.control(lprec, sense = 'max')  # this is a maximization problem

#Add the constraints
add.constraint(lprec, c(1,0,0,1,0,0,1,0,0), "<=", 750) 
add.constraint(lprec, c(0,1,0,0,1,0,0,1,0), "<=", 900)
add.constraint(lprec, c(0,0,1,0,0,1,0,0,1), "<=", 450)
add.constraint(lprec, c(20,0,0,15,0,0,12,0,0),"<=",13000)
add.constraint(lprec, c(0,20,0,0,15,0,0,12,0), "<=", 12000)
add.constraint(lprec, c(0,0,20,0,0,15,0,0,12),"<=", 5000)
add.constraint(lprec,c(1,1,1,0,0,0,0,0,0), "<=", 900) 
add.constraint(lprec, c(0,0,0,1,1,1,0,0,0), "<=",1200)
add.constraint(lprec, c(0,0,0,0,0,0,1,1,1), "<=", 750)
add.constraint(lprec, c(900,-750,0, 900,-750,0,900,-750,0),"=",0)
add.constraint(lprec, c(0,450,-900,0,450,-900,0,450,-900),"=",0)

#set variable names and name the constraints
RowNames <- c("Capacity1", "Capacity2", "Capacity3", "Storage1","Storage2",
              "Storage3","Sale1","Sale2","Sale3","Perc1","Perc2")
ColNames <- c("L1", "L2", "L3","M1","M2","M3", "S1","S2","S3")
dimnames(lprec) <- list(RowNames, ColNames)

# The model can also be saved to a file
write.lp(lprec, filename = "wliu16.lp", type = "lp")

x <- read.lp("wliu16.lp") # create an lp object x
x 
```

```{r}
solve(lprec)
```

The objective function is 696,000

```{r}
get.objective(lprec)
get.variables(lprec)
```
The 9 variables are 516.6667, 0, 0, 177.7778, 666.6667, 0,0, 166.6667, 416.6667

In conclusion if considering first 9 constraints:
The optimal output is 708000 and 9 variables are 
350.0000   0.0000   0.0000 400.0000 400.0000 133.3333   0.0000 500.0000 250.0000
Plant1 produces 350 large and 400 medium products
Plant2 produces 400 medium and 500 small products
Plant3 produces 133.3333 medium and 250 small products

If considering all 11 constraints,the optimal max profit is 696,000
Plant1 produces 516.6667 large and 177.7778 medium products, 
Plant2 produces 666.6667 medium and 166.6667 small products
Plant3 produces 416.6667 small products.
If the number of products are integers, we will take a neighboring set of 
the optimal that can satisfy the percentage constraint approx (not 100%). 
Plant1 can produce 516 large and 177 medium products. 
Plant 2 should produce 666 medium and 166 small products while 
Plant 3 should produce 416 small products to reach a max profit of 694,800

$$Z = 420* 516 + 360*(177+ 666) + 300*(166+416) = 694,800$$

