---
title: "Assignment 4 module 8"
author: "wliu16"
date: "2022-10-31"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Benchmarking)
```

```{r}
#format the problem
tab <- matrix(c("Facility 1","Facility 2","Facility 3","Facility 4","Facility 5",
                "Facility 6",
              150,400,320,520,350,320,
              0.2,0.7,1.2,2.0,1.2,0.7,
              14000,14000,42000,28000,19000,14000,
              3500,21000,10500,42000,25000,15000), ncol=5, byrow=F)
colnames(tab) <- c('DMU', 'Staff Hour per Day','Supplies per Day','Reimbursed patient-days',
                   'Privately Paid Patient-Days')
tab <- as.table(tab)
tab
```

***1. Formulate and perform DEA of FDH, CRS, VRS, IRS, DRS, and FRH.***
***2. Determine the Peers and Lambdas under each of the above assumptions***
```{r}
#Input format
x<-matrix(c(150,400,320,520,350,320,
              0.2,0.7,1.2,2.0,1.2,0.7), 
          ncol = 2)
y<-matrix(c(14000,14000,42000,28000,19000,14000,
              3500,21000,10500,42000,25000,15000),
          ncol=2)
colnames(y)<-c('Reimbursed patient-days', 'Privately Paid Patient-Days')
colnames(x)<-c('Staff Hour per Day','Supplies per Day')

#Scale: CRS, IRS, DRS, VRS
dea(x,y,RTS="crs")
e<-dea(x,y,RTS = "crs")
e
peers(e)
lambda(e)
```
CRS Observation:
Facility 1, 2, 3, 4 are efficient. Facility 5 is 97.75% efficient and facility 6
is 86.75 efficient. Both facility 5 and 6 use peer reference of facility 1, 2 and
4. The weights of facility 1, 2, 4 to facility 5 are 0.2, 0.08 and 0.54;
The weights of the same facilities to facility 6 are 0.34, 0.39, and 0.13

```{r}
dea(x,y,RTS="irs")
e<-dea(x,y,RTS = "irs")
e
peers(e)
lambda(e)
```
IRS Observation:
Facility 1, 2, 3, 4, 5 are efficient. Facility  6 is 89.63 efficient and uses 
facility 1, 2 and 5 as peer references. The weights of facility of 1, 2, and 5
to facility 6 are 0.4, 0.34 and 0.26
```{r}
dea(x,y,RTS="drs")
e<-dea(x,y,RTS = "drs")
e
peers(e)
lambda(e)
```
DRS Observation:
Facility 1, 2, 3, 4 are efficient. Facility 5 is 97.75 efficient and Facility 6 
is 86.75 efficient. Both use facility 1, 2 and 4 as peer references.
The weights of facility 1, 2, 4 to facility 5 are 0.2, 0.08 and 0.54;
The weights of the same facilities to facility 6 are 0.34, 0.39, and 0.13

```{r}
dea(x,y,RTS="vrs")
e<-dea(x,y,RTS = "vrs")
e
peers(e)
lambda(e)
```
VRS Observation:
Facility 1, 2, 3, 4, 5 are efficient. Facility  6 is 89.63 efficient and uses 
facility 1, 2 and 5 as peer references. The weights of facility of 1, 2, and 5
to facility 6 are 0.4, 0.34 and 0.26
```{r}
#Free disposability FDH and free replicability FRH
dea(x,y,RTS="fdh")
e<-dea(x,y,RTS = "fdh")
e
peers(e)
lambda(e)

dea(x,y,RTS="fdh+")
e<-dea(x,y,RTS = "fdh+")
e
peers(e)
lambda(e)
```
FDH and FRH Observation:
Both share the same results. All facilities are efficient in both methods.

***3. Summary of results in tabular format***
```{r}
summary_tab <- matrix(c("Facility 1","Facility 2","Facility 3","Facility 4","Facility 5",
                "Facility 6", "Peer set",
              1,1,1,1,0.9775, 0.8675, "1,2,4",
              1,1,1,1,0.9775, 0.8675, "1,2,4",
              1,1,1,1,1,0.8963, "1,2,5",
              1,1,1,1,1,0.8963,"1,2,5",
              1,1,1,1,1,1,"NA",
              1,1,1,1,1,1, "NA"), ncol=7, byrow=F)
colnames(summary_tab) <- c('DMU', 'CRS','DRS','IRS','VRS', 'FDH','FRH')
summary_tab <- as.table(summary_tab)
summary_tab
```
<br/ >
<br/ >
Comments:
1 means efficient. Since Facility 5 and 6 always have the same peer set, we 
use one peer set to refer to each method.

***4. Compare and contrast the above results***

```{r}
dea.plot(x,y,RTS="vrs",ORIENTATION="in-out",txt=TRUE, 
         xlab = "Input", ylab ="Output")
dea.plot(x,y,RTS="drs",ORIENTATION="in-out",add=TRUE,lty="dashed",lwd=2,col="yellow")
dea.plot(x,y,RTS="irs",ORIENTATION="in-out",add=TRUE,lty="dotted",lwd=2, col="red")
dea.plot(x,y,RTS="crs",ORIENTATION="in-out",add=TRUE,lty="dotted",lwd=2, col="blue")
dea.plot(x,y,RTS="fdh",ORIENTATION="in-out",txt=TRUE,main="fdh",
         xlab = "Input", ylab ="Output")
dea.plot(x,y,RTS="fdh+",ORIENTATION="in-out",add=TRUE,lty="dotted",param=.5)
```
